A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-24 main.tex
分割コンパイルが失敗する
Fix a bug.
Move proofs to a separate file and share with main.tex.
Add the example of vadd function to Section 2.
Add some comments on the writing style for proofs.
Move full definition to text/fulldefinition.tex and tidy up.
FInish revising Seciton 1.
Shorten the introduction.
Spellcheck (except proof.tex)
Tidy up Weakening.
Fixing proofs.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\newif\ifnotanonymous \notanonymousfalse
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
\usepackage{lscape}
\usepackage{mdframed}
\usepackage{xspace}

@@

\newcommand{\KVar}{\textsc{K-Var}}
\newcommand{\KAbs}{\textsc{K-Abs}}
\newcommand{\KApp}{\textsc{K-App}}
\newcommand{\KConv}{\textsc{K-Conv}}
\newcommand{\KTW}{\textsc{K-$\TW$}}
\newcommand{\KTWL}{\textsc{K-$\TWL$}}
\newcommand{\KGen}{\textsc{K-Gen}}
\newcommand{\KCsp}{\textsc{K-Csp}}

@@

@@

\blue{181 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
\blue{コードとかはボールドを使ったほうが良いかもしれない。}
\red{Suspicious senetences are colored red.}
%
%
%
\red{Multi-stage Programming と Multi-stage Calculus をどう使い分けるか?}

\input{introduction.tex}

\input{informal-overview.tex}

\input{formal-defnition.tex}

\input{properties.tex}

\input{related-work.tex}

\input{conclusions.tex}

@@

\section{Appendix}

\blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies. Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures. This category encompasses both theoretical and implementation (also known as system descriptions) papers. In either case, submissions should clearly identify what has been accomplished and why it is significant. Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity. System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design. In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
\blue{Review Process
	APLAS 2019 will use a lightweight double-blind reviewing process. Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper. The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
	To facilitate this process, submitted papers must adhere to the following:
	Author names and institutions must be omitted and
	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try. Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas. For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure. Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would. For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
\end{document}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\newif\ifnotanonymous \notanonymousfalse
\newif\iffullversion \fullversiontrue
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
\usepackage{lscape}
\usepackage{xspace}
\usepackage{url}

@@

\newcommand{\KVar}{\textsc{K-Var}}
\newcommand{\KTConst}{\textsc{K-TConst}}
\newcommand{\KAbs}{\textsc{K-Abs}}
\newcommand{\KApp}{\textsc{K-App}}
\newcommand{\KConv}{\textsc{K-Conv}}
\newcommand{\KTW}{\textsc{K-$\TW$}}
\newcommand{\KTWL}{\textsc{K-$\TWL$}}
\newcommand{\KGen}{\textsc{K-Gen}}
\newcommand{\KCsp}{\textsc{K-Csp}}

@@

\newcommand{\rulefbox}[1]{\fbox{\ensuremath{#1}} \hspace{1mm}}

@@

\input{text/introduction.tex}

\input{text/informal-overview.tex}

\input{text/formal-defnition.tex}

\input{text/properties.tex}

\input{text/related-work.tex}

\input{text/conclusion.tex}

@@

\iffullversion
\appendix

%\newtheorem{thm}{Theorem}
\newtheorem{dfn}{Definition}
\newtheorem{ex}{Example}
\newtheorem{cm}{Comment}
\newcommand{\figheader}[2]{
  \begin{flushleft}
    #2 {\bf \normalsize #1}
\end{flushleft}}

\newpage
\section{Full Definition of \LMD}
\input{text/fulldefinitions}

\section{Proofs}
\input{text/proofs}

\fi
% \section{Appendix}

% \blue{We solicit submissions in the form of regular research papers describing original scientific research results, including system development and case studies. Regular research papers should not exceed 18 pages in the Springer LNCS format, including bibliography and figures. This category encompasses both theoretical and implementation (also known as system descriptions) papers. In either case, submissions should clearly identify what has been accomplished and why it is significant. Submissions will be judged on the basis of significance, relevance, correctness, originality, and clarity. System descriptions papers should contain a link to a working system and will be judged on originality, usefulness, and design. In case of lack of space, proofs, experimental results, or any information supporting the technical results of the paper could be provided as an appendix or a link to a web page, but reviewers are not obliged to read them.}
% \blue{Review Process
% 	APLAS 2019 will use a lightweight double-blind reviewing process. Following this process means that reviewers will not see the authors’ names or affiliations as they initially review a paper. The authors’ names will then be revealed to the reviewers only once their reviews have been submitted.
% 	To facilitate this process, submitted papers must adhere to the following:
% 	Author names and institutions must be omitted and
% 	References to the authors’ own related work should be in the third person (e.g., not “We build on our previous work …” but rather “We build on the work of …”).
% 	The purpose of this process is to help the reviewers come to an initial judgement about the paper without bias, not to make it impossible for them to discover the authors if they were to try. Nothing should be done in the name of anonymity that weakens the submission, makes the job of reviewing the paper more difficult, or interferes with the process of disseminating new ideas. For example, important background references should not be omitted or anonymized, even if they are written by the same authors and share common ideas, techniques, or infrastructure. Authors should feel free to disseminate their ideas or draft versions of their paper as they normally would. For instance, authors may post drafts of their papers on the web or give talks on their research ideas.}
\end{document}
